---
title: "R to Python"
author: "Prithviraj Lakkakula"
date: "7/25/2022"
output:
  html_document: 
    toc: yes
    highlight: zenburn
    theme: cosmo
  pdf_document: 
    toc: yes
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(reticulate)
#https://www.geeksforgeeks.org/python-set-operations-union-intersection-difference-symmetric-difference/
```

<!--
:::: {style="display: grid;"} ### this code if you add below will display one after the other top and bottom.
#For more info, see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html
-->

# Basics of Programming

## Creating a dataframe 

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
# construct a dataframe
df <- data.frame(a = c(1, 2, 3, 4, 5),
                 b = c(3, 4, 5, 6, 7))
df
```

:::

::: {}
Python code

```{python}
import pandas as pd
df = pd.DataFrame({'a': [1, 2, 3, 4, 5],
                          'b': [3, 4, 5, 6, 7]})
print(df)
```
:::

::::

## Imports

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
sqrt(36)
```

:::

::: {}
Python code

```{python}
import math
math.sqrt(36)

#importing a function
from math import sqrt
sqrt(36)

# show all functions in math model
print(dir(math))
```
:::

::::

## Data Types

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
class(5)
class(5.0)
class('Five')
class(FALSE)

## check if an object is of a given type
is.numeric(5)
is.character('Five')
is.logical(FALSE)

## Convert an object to a given type
as.character(5.5)
#as.numeric, as.factor etc to convert to numeric and factor types
```

:::

::: {}
Python code

```{python}
type(5)
type(5.0)
type('five')
type(False)

## check if an object is of a given type
isinstance(5.0, int)
isinstance(5.0, (int, float))
isinstance('Five', str)
isinstance('Five', int)
isinstance(False, bool)

## Convert an object to a given type
str(5.5)
```
:::

::::

## Basic Math

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
5 + 4 #addition
5 - 4 #subtraction
5 * 4 #multiplication
5 ^ 4 #exponent
5 %% 4 # divides and remainder is the output. modulo
100 / 4 #division
floor(100 / 3) #returns floor
ceiling(100 / 3)
```

:::

::: {}
Python code

```{python}
import math
5 + 4 #addition
5 - 4 #subtraction
5 * 4 #multiplication
5 ** 4 #exponent
5 % 4 # divides and remainder is the output. modulo
100 / 4 #division
100 // 3 #returns floor #math.floor(100 / 3) also returns the same
math.ceil(100 / 3)
```
:::

::::

## Comparisons and Boolean Operations

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
## Assignment statement
x <- 10

## comparisons
x > 10
x >= 10
x != 10
x == 7

## Boolean operations
6 > 4 & 5 > 4
6 > 4 | 5 > 4
!FALSE
FALSE | !FALSE & TRUE #evaluation order: ! (not), & (and), | (or)
```

:::

::: {}
Python code

```{python}
## Assignment statement
x = 10

## comparisons
x > 10
x >= 10
x != 10
x == 7

## Boolean operations
6 > 4 and 5 > 4
6 > 4 or 5 > 4
not False
False or not False and True #evaluation order: ! (not), & (and), | (or)
```
:::

::::

## Conditional Statements

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
## if statement
x <- 10
if (x > 0) {#condition
  print("success") #statement
}  

## if/else statement
if (x > 0){
  print("success")} else {
  print("not success")
  }

## if/elif/else statement
if (x > 0){
  print("success")
} else if (x == 0) {
  print("not success")
} else {
  print("not so success")
}
```

:::

::: {}
Python code

```{python}
## if statement
x = 10
if x > 0:
  print('success')
  
## if/else statement
if x > 0:
  print('success')
else:
  print('not success')

## if/elif/else statement
if x > 0:
  print('success')
elif x == 0:
  print('not success')
else:
  print('not so success')
```
:::

::::

## Lists

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
### empty list
empty_list <- list()
empty_list

## creating a list
create_list <- list("he", "she", "him")
create_list

## print 1st and 3rd element of create list
create_list[[1]] #R follows 1-indexing
create_list[[3]]

## length of the list
length(create_list)

## appending the list

create_list[[4]] <- "her"
create_list

create_list <- append(create_list, c("me", "you"))
create_list 
str(create_list)
```

:::

::: {}
Python code

```{python}
## empty list
empty_list = []
empty_list2 = list()
empty_list
empty_list2

## create a list
create_list = ['he', 'she', 'him']
create_list

## print 1st and 3rd element of create list
create_list[0] #python follows zero-indexing
create_list[2]

## length of a list
len(create_list)

## appending the list
create_list.append('her')
create_list.extend(['me', 'you'])
create_list
type(create_list)
```
:::

::::



## Importing data from a variety of data formats

## How to call heads and tails?

## How to know the shape/length of the data?

## How to access single and multiple columns?

## Get summary stats of the data variables

## How to graph plots (scatter plot, histogram, boxplot, barplot etc.)?

## Handling missing values?

## Handling outliers?

## Checking class imbalance?

## Splitting the dataset into training and test sets for both cross section and time series data cases?

## Run a linear regression model along with predictions on test set, model evaluation, performance metrics?

## Run a logistic regression model along with predictions on test set, model evaluation, performance metrics?


