---
title: "R to Python"
author: "Prithviraj Lakkakula"
date: "7/25/2022"
output:
  pdf_document: 
    toc: yes
    highlight: zenburn
  html_document: 
    toc: yes
    highlight: zenburn
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
library(reticulate)
#https://www.geeksforgeeks.org/python-set-operations-union-intersection-difference-symmetric-difference/
```

<!--
:::: {style="display: grid;"} ### this code if you add below will display one after the other top and bottom.
#For more info, see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html
-->


## Creating a dataframe and performing set operations

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}


::: {}

R code

```{r warning=FALSE, message=FALSE}
# construct a dataframe
df <- data.frame(a = c(1, 2, 3, 4, 5),
                 b = c(3, 4, 5, 6, 7))
df
#intersect(df$a, df$b)
```

:::

::: {}
Python code

```{python}
import pandas as pd
df = pd.DataFrame({'a': [1, 2, 3, 4, 5],
                          'b': [3, 4, 5, 6, 7]})
df
#set(df['a']) & set(df['b'])
```
:::

::::



## Importing data from a variety of data formats

## How to call heads and tails?

## How to know the shape/length of the data?

## How to access single and multiple columns?

## Get summary stats of the data variables

## How to graph plots (scatter plot, histogram, boxplot, barplot etc.)?

## Handling missing values?

## Handling outliers?

## Checking class imbalance?

## Splitting the dataset into training and test sets for both cross section and time series data cases?

## Run a linear regression model along with predictions on test set, model evaluation, performance metrics?

## Run a logistic regression model along with predictions on test set, model evaluation, performance metrics?


